Efficient implementation of kernel filtering

### 2007-08-02 article/Article.tex
some extensions to the article
darcs-hash:20070802141347-2fc9d-b5b8e1950a02fbb3c99701598da470077a334bfc.gz

@@

The morphology filters utilize a new class -- {\em
FlatStructuringElement} to describe, arbitary and decomposable
structuring elements. It provides the following methods to create
structuring elements with different characteristics:
\begin{itemize}
  \item \verb$Ball()$ generate a ball structuring element (a circle in 2D). It takes the 
	radius of the structuring element as parameter.
  \item \verb$Box()$ produces a box structuring element. It takes the radius 
	of the structuring element as parameter.
  \item \verb$Poly()$ produces an approximation to a circle or sphere using 
	line structuring elements, taking the desired radius and number of 
	lines as parameters. In the 3D case an approximation of a sphere will 
	be attempted. Caution is advised because this is not well tested yet.
  \item \verb$FromImage()$ produces a structuring element from an image. The image is passed
as parameter to the method. A optional parameter can also be passed: the pixel value
to be considered as the foreground value in the image. This value defaults to
\verb$NumericTraits< PixelType >::max()$. This lets the user visualize the structuring element.
\end{itemize}

@@

All the kernel based filters in ITK would also benefit to hinerit a common
super class which manage the neighborhood size and/or the kernel, and which
provide the infrastructure for the separable operations.

>>>>

\subsection{Common filters}

All the filters provided with those packages are implemented as subclasses
of one of two new classes: {\em itk::BoxImageFilter} and {\em itk::KernelImageFilter}.
{\em itk::BoxImageFilter} is a subclass of {\em itk::ImageToImageFilter} and provides
some features used in all the box based filters:
\begin{itemize}
  \item the management of the radius of the box,
  \item and the enlargement of the input requested region, according to the box size.
\end{itemize}
{\em itk::KernelImageFilter} is a subclass of {\em itk::BoxImageFilter}, and provides
some features used in all the kernel based filters, in addition to the features of the
{\em itk::BoxImageFilter} class:
\begin{itemize}
  \item the management of the kernel,
  \item a redefined SetRadius() method to create a box kernel with the provided radius,
  \item a default box kernel of radius $1$\footnote{This feature should help many ITK
beginers who are often {\em not} providing a structuring element to the morphology filters,
and thus get difficultly understandable crashes.}.
\end{itemize}

A third filter, {\em itk::SeparableImageFilter}, is used to easily implement a separable
version of an algorithm, by using its basic implementation in a subclass of
{\em itk::BoxImageFilter}, or any other subclass of {\em ImageToImageFilter} with
a {\em SetRadius()} method.

Some filters already in ITK have been modified to use {\em itk::BoxImageFilter} or
{\em itk::KernelImageFilter}\footnote{itk::MedianImageFilter, itkMeanImageFilter,
itk::NoiseImageFilter and itk::MorphologyImageFilter.}. Their API is not modified.

@@

The morphology filters utilize a new class -- {\em
FlatStructuringElement} to describe, arbitary and decomposable
structuring elements. It provides the following methods to create
structuring elements with different characteristics:
\begin{itemize}
  \item \verb$Ball()$ generate a ball structuring element (a circle in 2D). It takes the 
	radius of the structuring element as parameter.
  \item \verb$Box()$ produces a box structuring element. It takes the radius 
	of the structuring element as parameter.
  \item \verb$Poly()$ produces an approximation to a circle or sphere using 
	line structuring elements, taking the desired radius and number of 
	lines as parameters. In the 3D case an approximation of a sphere will 
	be attempted. Caution is advised because this is not well tested yet.
  \item \verb$Cross()$ produces a cross structuring element. It takes the radius 
	of the structuring element as parameter.
  \item \verb$Annulus()$ produces an annulus structuring element. It takes the radius 
	of the structuring element as parameter, as well as the thickness of the annulus,
	and a boolean to indicate whether the center neighbors should be set inside the
	neighborhood or not\footnote{The {\em Annulus()} constructor  is a contribution
of Dan Mueller.}.
  \item \verb$FromImage()$ produces a structuring element from an image. The image is passed
as parameter to the method. A optional parameter can also be passed: the pixel value
to be considered as the foreground value in the image. This value defaults to
\verb$NumericTraits< PixelType >::max()$. This lets the user visualize the structuring element.
\end{itemize}

@@
